Assignment 3

### 2015-02-17 rmtw/a3/latex8.tex
Removed itemize, fixed issues in design and prep sections

\SubSection{Case Company Description}
The subject case organisation in this study is Ericsson. Ericsson operates in the domain of communications technology, and their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}. Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development). \cite{a7}.

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.

@@

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias. The random sampling was done on official employee records. The number of subjects for the interviews was (XXX or were?) 15. The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed. The main reason the three different roles were included was to be able to reduce research bias through data triangulation.

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\end{itemize}

>>>>

\SubSection{Case Company Description}
The subject case organisation in this study is Ericsson AB. Ericsson operates in the domain of communications technology, their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}. Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development). \cite{a7}.

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackles the problems related to the research questions has been the central part of the study. Due to the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.

@@

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias but does eliminate it. Random sampling was performed on official employee records. 15 employees were chosen to be the subjects for the interviews. The subjects were divided into three sub-groups; managers, developers and change agents with 5 of each role being interviewed. The main reason the three different roles were included was to be able to reduce research bias through data triangulation.

@@
